---
title: "DATA 607 Assignment 3"
author: "Fan Xu"
date: "9/14/2019"
output:
  pdf_document:
        extra_dependencies: ["geometry", "multicol", "multirow"]
  html_document:
    df_print: paged
    toc: yes
    toc_collapsed: yes
    toc_float: yes
theme: lumen
number_sections: yes
toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 3 

Copy the introductory example. The vector name stores the extracted names.

[1] "Moe Szyslak"  "Burns, c. Montgomery"  "Rev. Timothy Lovejoy" <br/>

[2] "Ned Flanders" "Simpson, Homer"        "Dr. Julius Hibbert" <br/>

**(a). Use the tools of this chapter to rearrange the vector so that all elements conform to the standard.** <br/>

first_name last_name.<br/>

Answer:<br/>
```{r Problem 3 #1}
library(stringr)
raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
names <- unlist(str_extract_all(raw.data,"[[:alpha:]., ]{2,}"))
names
#First remove possible title then switch first name and last name if last name come in first
first_last <-str_replace(str_replace(names,"^\\w{2,3}\\. ",""),"(\\w+), (.+)","\\2 \\1")
first_last
```


**(b). Construct a logical vector indicating whether a character has a title(i.e., Rev. and Dr.).**<br/>
Answer:<br/>
```{r Problem 3 #2}
# use str_detect function to construct the logical (boolean) vector
hastitle <- str_detect(names,"^\\w{2,3}\\. ")
hastitle
names[hastitle == TRUE]
```



**(c). Construct a logical vector indicating whether a character has a second name.**<br/>
Answer:<br/>
```{r Problem 3 #3}
#again use str_detect function to construct the logical (boolean) vector
#we can locate the character who has a second name from the original name list 
has2ndname1<-str_detect(names, "[:upper:]. ")
has2ndname1
names[has2ndname1 == TRUE]

#or we can locate the character from the ordered name list from Problem 3.1
has2ndname2 <-str_detect(first_last, ".+ .+ .+")
has2ndname2
first_last[has2ndname2 == TRUE]
```

# Problem 4 
**Describe the types of strings that conform to the following regular expressions and
construct an example that is matched by the regular expression.**<br/>


**(a) [0-9]+\\$ <br/>**
Answer:<br>
The strings that conform to (a) are with one or more digits plus one dollar sign. "[0-9]" means to match only number 0 to 9. "+" means match the preceding item one or more times, which refer to [0-9] here. The 2 backslashes before "$" means to treat the dollar sign as a character instead of a metacharacter.
``` {r Problem 4 (a)}
str_detect("A12390$abc", "[0-9]+\\$")
str_extract("A12390$abc", "[0-9]+\\$")
```


**(b) \\b[a-z]{1,4}\\b** <br/>
Answer:<br>
The strings that conform to (b) are with a word of 1 to 4 lower case letters and empty string at either edge of this word. "\\b" means empty string at either side of a word, "[a-z]" means to match all lower case letters, "{1,4}" means to match the preceding item between 1 to 4 times.
``` {r Problem 4 (b)}
str_detect("123 abcd ABC", "\\b[a-z]{1,4}\\b")
str_extract("123 abcd ABC", "\\b[a-z]{1,4}\\b")
```


(c) .\*?\\.txt$ <br/>
Answer:<br/>
The string that conform to (c) are any strings that contain ".txt" at the end. "." means to match any character except the new line indicator "\n". "*" means to match the preceding item 0 or more times. "?" means the preceding item is optional and to matches at most one time. The double backslashes before "." treat the period sign as an character steadn of a metacharacter. the "$" before ".txt" means the pattern ".txt" only exists at the end of the string if matched.
``` {r Problem 4 (c)}
str_detect("abcd123.txtcdfg456.txt", ".*?\\.txt$")
str_extract("abcd123.txtcdfg456.txt", ".*?\\.txt$")
```


**(d) \\d{2}/\\d{2}/\\d{4}** <br/>
Answer:<br>
The string that conform to (d) contain digits and slash sign "/" conbination of pattern like date format "00/00/0000". "\\d" means to match digits 0 to 9.
``` {r Problem 4 (d)}
str_detect("Today is 19/19/1919 do you believe?", "\\d{2}/\\d{2}/\\d{4}")
str_extract("Today is 19/19/1919 do you believe?", "\\d{2}/\\d{2}/\\d{4}")
```


**(e) <(.+?)>.+?</\\1>** <br>
Answer:<br>
the string that conform to (e) contain patterns like start tags and end tags in HTML OR XML, and all content in between. "." means to match any character except the new line indicator "\n". "+" means to match the preceding item last least 1 time. "?" means the preceding item is optional and to matches at most one time. the parenthesis "()" performs a grouping function and enables back referencing using \\N where N is an integer. "//1" back references to the first group content (here the only group) matched by ".+?"
``` {r Problem 4 (e)}
str_detect("abcde<tagname>xxx11223344aabbcc</tagname>fghij", "<(.+?)>.+?</\\1>")
str_extract("abcde<tagname>xxx11223344aabbcc</tagname>fghij", "<(.+?)>.+?</\\1>")
```

# Problem 9

**The following code hides a secret message. Crack it with R and regular expressions.
Hint: Some of the characters are more revealing than others! The code snippet is also
available in the materials at www.r-datacollection.com.** <br/>

clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0Tanwo
Uwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigO
d6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5
fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr

``` {r Problem 9}
code <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0Tanwo
Uwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigO
d6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5
fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"
#Extract all upper case letters and punctuation marks
decode <- unlist(str_extract_all(code, "[[:upper:][:punct:]]"))
decode
#make it nicer :)
str_replace_all(str_c(c(decode,"!!"), collapse= ""),"\\."," ")
```
